Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-06-28 hazelnut-popl17.tex
adding some todos

%  \emph{Structure editors} have long promised to alleviate these burdens by exposing only edit actions that  cause sensible changes to the program structure.
% Existing designs for structure editors, however, are complex and somewhat \emph{ad hoc}. They also focus primarily on syntactic well-formedness, so programs can still be left semantically meaningless as they are being constructed.
% Structure editors (e.g. Scratch) eliminate the possibility of syntax errors.

\emph{Structure editors} allow programmers to edit the tree structure of a program directly -- there are no syntax errors. This can have cognitive benefits, particularly for novice and end-user programmers (as evidenced by the popularity of structure editors like Scratch.) It also simplifies matters for tool designers, because they need not contend with malformed program text. %Structure editors for professional programmers are also under active development (e.g. \texttt{mbeddr}.)

@@

TODO: \url{http://research.nii.ac.jp/~hu/pub/hosc07.pdf}

@@

TODO: cite \url{http://cseweb.ucsd.edu/~lerner/pb.html}

TODO: cite \url{http://delivery.acm.org/10.1145/1060000/1056965/p1557-ko.pdf?ip=73.154.143.34&id=1056965&acc=AUTHOR-IZED&key=4D4702B0C3E38B35%2E4D4702B0C3E38B35%2E4D4702B0C3E38B35%2EC2CC0A83071F7605&CFID=780613712&CFTOKEN=33786941&__acm__=1462392463_f29fc98965004c61bfb1291d07756a23}

@@

>>>>

%  \emph{Structure editors} have long promised to alleviate these burdens by exposing only edit actions that  cause sensible changes to the program structure.
% Existing designs for structure editors, however, are complex and somewhat \emph{ad hoc}. They also focus primarily on syntactic well-formedness, so programs can still be left semantically meaningless as they are being constructed.
% Structure editors (e.g. Scratch) eliminate the possibility of syntax errors.
\todo{why not title just ``hazelnut: a structure editor calculus''?}
\emph{Structure editors} allow programmers to edit the tree structure of a program directly -- there are no syntax errors. This can have cognitive benefits, particularly for novice and end-user programmers (as evidenced by the popularity of structure editors like Scratch.) It also simplifies matters for tool designers, because they need not contend with malformed program text. %Structure editors for professional programmers are also under active development (e.g. \texttt{mbeddr}.)

@@

\todo{TODO: \url{http://research.nii.ac.jp/~hu/pub/hosc07.pdf}}

@@

\todo{TODO: cite \url{http://cseweb.ucsd.edu/~lerner/pb.html}}

\todo{TODO: cite} \url{http://delivery.acm.org/10.1145/1060000/1056965/p1557-ko.pdf?ip=73.154.143.34&id=1056965&acc=AUTHOR-IZED&key=4D4702B0C3E38B35%2E4D4702B0C3E38B35%2E4D4702B0C3E38B35%2EC2CC0A83071F7605&CFID=780613712&CFTOKEN=33786941&__acm__=1462392463_f29fc98965004c61bfb1291d07756a23}

@@

\todo{new action form that makes actions extensible given proofs of
admissiblity of a derived form, like prevSib}
